Probabilistic Programming around Gaussian Processes

### 2019-10-22 abstract/paper.tex
a couple typos fixed

In basic usage, the observation noise is assumed to be Gaussian.
This usage is supported by initializing \lstinline{GP} with a noise
kernel, along with a similarity kernel. When the noise is not
Gaussian~\cite{MWN+17}, an analytical solution for posterior Gaussian process
inference does not always exist. However, non-Gaussian noise is
straightforwardly supported by GoGP through supplying a
model for beliefs on observation outputs:
\begin{lstlisting}
type Noise struct {
	Y []float64 // noisy outputs
}
func (m *Noise) Observe(x []float64) float64 {
	// Laplacian noise
	for i := range m.Y {
		ll += Expon.Logp(1/math.Exp(x[0]),
			math.Abs(m.Y[i]-x[1+i]))
	}
	return ll
}
\end{lstlisting}

>>>>

In basic usage, the observation noise is assumed to be Gaussian.
This usage is supported by initializing \lstinline{GP} with a noise
kernel, along with a similarity kernel. When the noise is not
Gaussian~\cite{MWN+17}, an analytical solution for posterior Gaussian process
inference does not always exist. However, non-Gaussian noise is
straightforwardly supported by GoGP through supplying a
model for beliefs on observation outputs:
\begin{lstlisting}
type Noise struct {
	Y []float64 // noisy outputs
}
func (m *Noise) Observe(x []float64) (ll float64){
	// Laplacian noise
	for i := range m.Y {
		ll += Expon.Logp(1/math.Exp(x[0]),
			math.Abs(m.Y[i]-x[1+i]))
	}
	return ll
}
\end{lstlisting}
